Figure 5 - IP-MS

### 2024-08-18 ms_figure_5_ipms.Rmd
Suppress special character formatting warnings

```{r}
#| label: tstat-150-vs-500
#| fig.width: 6
#| fig.height: 7
#| message: false

@@

```{r}
df <- as.data.frame(rowData(sce150)) |>
    dplyr::select(einprotId, Atf1_150_tube_vs_compl_Atf1_150_tube.t, 
                  Atf1_150_plate_vs_compl_Atf1_150_plate.t) |>
    dplyr::mutate(col = ifelse(einprotId == "Atf1", "bait", 
                               ifelse(einprotId == "Pcr1", "Pcr1", "other")))
(ggatf1 <- ggplot(df, aes(x = Atf1_150_tube_vs_compl_Atf1_150_tube.t, 
                          y = Atf1_150_plate_vs_compl_Atf1_150_plate.t)) + 
        geom_abline(slope = 1, intercept = 0) + 
        geom_point(size = 3, aes(color = col, alpha = col)) + 
        scale_color_manual(values = c(bait = main_colors[3], pcr1 = main_colors[4], 
                                      other = "black")) + 
        scale_alpha_manual(values = c(bait = 1, pcr1 = 1, other = 0.5)) + 
        geom_text_repel(data = df |> filter(einprotId %in% c("Atf1", "Pcr1")), 
                        aes(label = einprotId)) + 
        labs(x = "Mod. t-stat. Atf1 vs complement\n(tube, 150 mM NaCl)", 
             y = "Mod. t-stat. Atf1 vs complement\n(plate, 150 mM NaCl)") + 
        coord_fixed() + 
        theme_cowplot() + 
        theme(legend.position = "none"))
```

@@

```{r Fig5}
#| fig.width: 9.8
#| fig.height: 14.5

>>>>

```{r}
#| label: tstat-150-vs-500
#| fig.width: 6
#| fig.height: 7
#| message: false
#| warning: false

@@

```{r}
#| warning: false

df <- as.data.frame(rowData(sce150)) |>
    dplyr::select(einprotId, Atf1_150_tube_vs_compl_Atf1_150_tube.t, 
                  Atf1_150_plate_vs_compl_Atf1_150_plate.t) |>
    dplyr::mutate(col = ifelse(einprotId == "Atf1", "bait", 
                               ifelse(einprotId == "Pcr1", "Pcr1", "other")))
(ggatf1 <- ggplot(df, aes(x = Atf1_150_tube_vs_compl_Atf1_150_tube.t, 
                          y = Atf1_150_plate_vs_compl_Atf1_150_plate.t)) + 
        geom_abline(slope = 1, intercept = 0) + 
        geom_point(size = 3, aes(color = col, alpha = col)) + 
        scale_color_manual(values = c(bait = main_colors[3], pcr1 = main_colors[4], 
                                      other = "black")) + 
        scale_alpha_manual(values = c(bait = 1, pcr1 = 1, other = 0.5)) + 
        geom_text_repel(data = df |> filter(einprotId %in% c("Atf1", "Pcr1")), 
                        aes(label = einprotId)) + 
        labs(x = "Mod. t-stat. Atf1 vs complement\n(tube, 150 mM NaCl)", 
             y = "Mod. t-stat. Atf1 vs complement\n(plate, 150 mM NaCl)") + 
        coord_fixed() + 
        theme_cowplot() + 
        theme(legend.position = "none"))
```

@@

```{r Fig5}
#| fig.width: 9.8
#| fig.height: 14.5
#| warning: false
